A Study on Online Sequential Learning using Bandits

### 2017-12-11 synopsis.tex
Latest on 11/12/2017

\textbf{The algorithm:} The Augmented-UCB (AugUCB) algorithm is presented in Algorithm~\ref{alg:augucb}.
AugUCB is essentially based on the arm elimination method of the UCB-Improved \citep{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}. However, unlike the UCB improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem. Further, we allow for arm-elimination at each time-step, which is in contrast to the earlier work (e.g., \cite{auer2010ucb,chen2014combinatorial}) where the arm elimination task is deferred to the end of the respective exploration rounds. The details are presented below.

@@

In chapter 1 (table \ref{tab:chap1}), we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions.

%\begin{center}
\begin{table}[!th]
\begin{center}
\begin{tabular}{|p{26em}|}
\hline\\
\textbf{1. Introduction to Bandits} \\\hline
1.1 Reinforcement Learning \\
1.2 Connection between Reinforcement Learning and Bandits \\
1.3 Why study Bandits?\\
1.4 Motivation \\
1.5 Types of Information Feedback\\
1.6 Different types of Bandits\\
1.7 Objectives of Thesis\\
1.8 Contributions of Thesis\\
1.9 Outline of the Thesis\\
\hline
\end{tabular}
\end{center}
\caption{Introduction to thesis}
\label{tab:chap1}
\end{table}
%\end{center}

>>>>

\textbf{The algorithm:} The Augmented-UCB (AugUCB) algorithm is presented in Algorithm~\ref{alg:augucb}.
AugUCB is essentially based on the arm elimination method of the UCB-Improved \citep{auer2010ucb}, but adapted to the thresholding bandit setting proposed in \cite{locatelli2016optimal}. However, unlike the UCB-Improved (which is based on mean estimation) our algorithm employs \emph{variance estimates} (as in \cite{audibert2009exploration}) for arm elimination; to the best of our knowledge this is the first variance-aware  algorithm for the thresholding bandit problem. Further, we allow for arm-elimination at each time-step, which is in contrast to the earlier work (e.g., \cite{auer2010ucb,chen2014combinatorial}) where the arm elimination task is deferred to the end of the respective exploration rounds. The details are presented below.

@@

In chapter 1 (table \ref{tab:chap1}), we discuss on Reinforcement Learning and its connection to bandits, we give an overview of the various types of bandits available in the literature and also discuss about the main objectives of the thesis and our contributions. Appendix A provides some useful results on Concentration inequalities.

%\begin{center}
\begin{table}[!th]
\begin{center}
\begin{tabular}{|p{26em}|}
\hline\\
\textbf{1. Introduction to Bandits} \\\hline
1.1 Reinforcement Learning \\
1.2 Connection between Reinforcement Learning and Bandits \\
1.3 Why study Bandits?\\
1.4 Motivation \\
1.5 Types of Information Feedback\\
1.6 Different types of Bandits\\
1.7 Objectives of Thesis\\
1.8 Contributions of Thesis\\
1.9 Outline of the Thesis\\
2.0 Appendix A\\
\hline
\end{tabular}
\end{center}
\caption{Introduction to thesis}
\label{tab:chap1}
\end{table}
%\end{center}
